MS Depression Paper, post replication, started 2022 09 21

### 2022-11-05 msdepression/scripts/MS_Depression_First_Paper_started_20220728/msdepression_n380_started_2022110222_post_replication_playing_w_graphs.Rmd
changing wrap graph

diagnosis_and_interaction_bar_combined <- ggarrange(bar_dep_vs_nondep_scaled_by_network_size,interaction_ggplot_bar, 
                                                labels = c("A", "B"),
                                                ncol = 2, nrow = 1)

>>>>

diagnosis_and_interaction_bar_combined <- ggarrange(bar_dep_vs_nondep_scaled_by_network_size,interaction_ggplot_bar, 
                                                labels = c("A", "B"),
                                                font.label = list(size = 16, color = "black", family = NULL),
                                                vjust = 9,
                                                ncol = 2, nrow = 1)
